%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% CV Jakša Tomović 06/2019 %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,letter]{altacv}

%Layout
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}

%Colors

\definecolor{accent}{HTML}{000e17}
\definecolor{heading}{HTML}{000e17}
\definecolor{emphasis}{HTML}{696969}
\definecolor{body}{HTML}{01415f}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%

\begin{document}
\name{Leila Abdelrahman}
\tagline{}
%\photo{2.5cm}{BrunoAlves}
\personalinfo{

 \small{Aspiring AI Researcher and Software Engineer. Experience gaining insights in data by developing machine learning algorithms, websites, and mobile applications.}
 \\
 \bigskip
    \email{\href{mailto:lxa215@miami.edu}{lxa215@miami.edu}}
    \phone{305-613-6819}
%    \mailaddress{SR Njemačke 6, 10000}
 %   \location{Zagreb, Croatia}
 %   \linkedin{linkedin.com/in/jaksatomovic}
    \homepage{\href{http://www.leilaabdel.com/}{leilaabdel.com}}
    \github{\href{https://github.com/lxa215}{github.com/lxa215}}
    
    
   
}

%

\begin{fullwidth}
\makecvheader
\end{fullwidth}

%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page1sidebar]{Experience}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Full Stack Developer}{University of Miami}{November 2019 -- Ongoing}{Miami, FL}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]   \small{Developed mobile iOS and Android applications for doctors to use nomograms for patient outcome prediction.}
    \item[--]   \small{Used knowledge of machine learning as back-end for the user-interface.}
    \item[--]   \small{Implemented HTML, Swift, and Kotlin to build web and mobile versions.}
    \item[--]   \small{Guided better doctor-patient discussions.}
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 2
%%%%%%%%%%%%%

\cvevent{AI Workshop Leader}{University of Miami}{November 2019 -- February 2020}{Miami, FL}

%\begin{itemize}
%    \item Fullstack JAVA developer
%\end{itemize}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]   \small{Developed lessons in Artificial Intelligence using Jupyter notebooks and TensorFlow.}
     \item[--] \small {Instructed students through simple perceptrons all the way to complex convolutions and transfer learning.}
    \item[--]   \small{Archived lessons to GitHub so they are open-access.}
   
\end{itemize}

\medskip

%%%%%%%%%%%%%
%Experience 3
%%%%%%%%%%%%%

\cvevent{Machine Learning Student Researcher}{University of Miami Miller School of Medicine}{October 2019 -- Ongoing}{Miami, FL}

%\begin{itemize}
%    \item Fullstack JAVA developer
%\end{itemize}

\begin{itemize}
    \setlength{\itemindent}{0.5em}
    \item[--]   \small{Designed data mining software and implemented machine learning algorithms to predict PEX and Glaucoma from metabolites.}
    \item[--]   \small{Submitted two publications to peer reviewed journals. Another is in progress.}
\end{itemize}

\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page2sidebar]{Projects}

%%%%%%%%%%%%%
%Project 1
%%%%%%%%%%%%%


\cvevent{Pipeline Program Data Scientist}{Florida International University}{December 2019 -- Ongoing}{Miami, FL}

\begin{itemize}
  \item Conducting analyses on student outcomes after participating in STEM pipeline programs throughout Miami-Dade county. 
  \item Utilizing natural language processing and R to understand trends in students' performance. 
\end{itemize}

\divider

%

%%%%%%%%%%%%%
%Project 2
%%%%%%%%%%%%%

\cvevent{Shifaa Electronic Medical Record System}{Service Project}{October 2019 -- Ongoing}{Alexandria, Egypt and Miami, FL}

\begin{itemize}
  \item \small{Developed an electronic medical record system GUI for Middle Eastern physicians with Visual Studio.}
  \item \small Full stack development ranging from UI design to relational database management.
    \item \small {Communicated with physicians so they can implement the application through GitHub into their clinics.}
  \item Techs: ASP.NET, Microsoft Azure, and SQL Server
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Certificates %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \cvsection{Certificates}

% %%%%%%%%%%%%%
% %Certificate 1
% %%%%%%%%%%%%%

% \cvevent{MCSD: App Builder — Certified 2019}{Microsoft}{Jan 2019 -- No Expiration Date}{}
% \divider

% %%%%%%%%%%%%%
% %Certificate 2
% %%%%%%%%%%%%%

% \cvevent{MCSA: Web Applications — Certified 2019}{Microsoft}{Jan 2019 -- No Expiration Date}{}
% \divider

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Interests %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \cvsection{Interests}

% \wheelchart{1.5cm}{0.5cm}{%
%   10/10em/accent!30/Electronics,
%   25/9em/accent!60/Science,
%   5/13em/accent!10/Movies,
%   20/15em/accent!40/Sport,
%   30/9em/accent/Technology,
%   5/8em/accent!20/Literature
% }


%%New Page
% \clearpage




\end{document}
